### 2009-12-14 docs/marcello-dissertation/thesis/chapter10-appendix.tex
Reviews of misspelling and references to pages, Section, etc.
- Chapter 7: Fixes on "Chapter" to chapter
- Chapter 8: Subversion Conflict line removal, and other fixes
- Appendix: Removing "on page x" for the image on the same page.

git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@706 559edde2-a4d4-44e0-96fc-4035e40d7396

The first experiment conducted was running the main experiment script of Listing
\ref{file:experiment-setup-executor}, as one of the execution runs shown in
Listing \ref{file:experiment-run.log}. The total number of inserted documents
measured every 20 seconds is displayed. Then, the execution of the use cases
was performed, as shown in Listing \ref{file:URD-scenarios-execution.log}.
Additional execution logs are shown in Section
\ref{sec:experiment-execution-logs}.

@@

The iterative mongo client shell offers users to verify and navigate on a
given database and its collections. This first section shows the connection of
the mongo client to the database ``netbeams'' as on Listing
\ref{cmd:mongodb-server-start}. The execution of the operation to count the
existing number of documents in the mongoDB collection ``netbeams'' is shown in
Listing \ref{cmd:mongodb-count}, page \pageref{cmd:mongodb-count}. It
highlights the query for the collections available in the netbeams database.

>>>>

The first experiment conducted was running the main experiment script of Listing
\ref{file:experiment-setup-executor} (page
\pageref{file:experiment-setup-executor}), as one of the execution runs shows
the results in Listing \ref{file:experiment-run.log}, page
\pageref{file:experiment-run.log}. The total number of inserted documents
measured every 20 seconds is displayed. Then, the execution of the use cases
was performed, as shown in Listing \ref{file:URD-scenarios-execution.log} page
\pageref{file:URD-scenarios-execution.log}. Additional execution logs are
shown in Section \ref{sec:experiment-execution-logs}.

@@

The iterative mongo client shell offers users to verify and navigate on a
given database and its collections. This first section shows the connection of
the mongo client to the database ``netbeams'' as on Listing
\ref{cmd:mongodb-server-start} on page \pageref{cmd:mongodb-server-start}. The
execution of the operation to count the existing number of documents in the
mongoDB collection ``netbeams'' is shown in Listing \ref{cmd:mongodb-count},
(page \pageref{cmd:mongodb-count}). It highlights the query for the collections
available in the netbeams database.
